---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# osmapiR

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

Implements [OpenStreetMap API](https://wiki.openstreetmap.org/wiki/API_v0.6) for R.

## Status

All `GET` calls implemented, also the ones requiring authentication. The server responses are parsed and transformed to
`data.frame`s. The format of the returned values still can change a bit.

## Installation

You can install the development version of osmapiR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jmaspons/osmapiR")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(osmapiR)

# For testing without breaking the OSM data, make calls to `https://master.apis.dev.openstreetmap.org`
set_osmapi_connection(server = "testing")
```
