---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# osmapiR

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/jmaspons/osmapiR/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/jmaspons/osmapiR/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/jmaspons/osmapiR/branch/main/graph/badge.svg)](https://codecov.io/gh/jmaspons/osmapiR)
[![pkgdown](https://github.com/jmaspons/osmapiR/actions/workflows/pkgdown.yaml/badge.svg)](https://github.com/jmaspons/osmapiR/actions/workflows/pkgdown.yaml)
<!-- badges: end -->

Implements [OpenStreetMap API](https://wiki.openstreetmap.org/wiki/API_v0.6) for R.

## Status

All API end points implemented. Requires testing and vignettes explaining the flow for editing.

## Installation

You can install the development version of osmapiR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jmaspons/osmapiR")
```

## Examples

This is a basic example which shows how to get map data:

```{r osm objects}
library(osmapiR)

# For testing edition without breaking the OSM data,
# make calls to `https://master.apis.dev.openstreetmap.org`

# set_osmapi_connection(server = "testing") # lacks data

bbox <- c(2.4166059, 42.5945594, 2.4176574, 42.5962101)

## Download objects by bounding box
osm_objs <- osm_bbox_objects(bbox = bbox, tags_in_columns = TRUE)

## View history of an object
sel <- osm_objs$`name:ca` %in% "Abadia de Sant Miquel de Cuixà"
obj <- osm_objs[sel, ]

obj_history <- osm_history_object(osm_type = obj$type, osm_id = obj$id) # tags in a list column
obj_history

# obj_history$tags
```


Get notes:
```{r notes}
notes <- osm_read_bbox_notes(bbox = bbox, closed = -1)
notes

# notes$comments
```


Get GPX data:
``` r
## Requires authentication
usr_traces <-  osm_list_gpxs()
osm_get_metadata_gpx(gpx_id = 3790367)
osm_get_data_gpx(gpx_id = 3790367, format = "R")
```
```{r gpx}
gpx <- osm_get_points_gps(bbox = bbox)
gpx
```


## Related packages

* [osmdata](https://cran.r-project.org/package=osmdata) implements the Overpass API to query data from OSM.
* [osmexctract](https://cran.r-project.org/package=osmextract) matches, downloads, converts and imports bulk OSM data
  (`.pbf` files)
* [OpenStreetMap](https://cran.r-project.org/package=OpenStreetMap) Accesses high resolution raster maps using the
  OpenStreetMap protocol.
  
`osmapiR` is the only package to access other OSM data than the maps data (map notes, GPS traces, changelogs and
users). It can be also useful to get the history of the OSM objects and is the only package that allows editing and
upload any kind of data.

To access the OSM map data for purposes other than editing or exploring the history of the objects, perhaps is better to
use the other packages that implements the Overpass API (`osmdata`) or that works with `.pbf` files (`osmexcract`).
