---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# osmapiR <a href="https://jmaspons.github.io/osmapiR"><img src="man/figures/logo.svg" align="right" height="200" alt="osmapiR website" /></a>

<!-- badges: start -->
[![R-CMD-check](https://github.com/jmaspons/osmapiR/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/jmaspons/osmapiR/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/jmaspons/osmapiR/branch/main/graph/badge.svg)](https://codecov.io/gh/jmaspons/osmapiR)
[![pkgdown](https://github.com/jmaspons/osmapiR/actions/workflows/pkgdown.yaml/badge.svg)](https://github.com/jmaspons/osmapiR/actions/workflows/pkgdown.yaml)
[![Project Status: Active](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/osmapiR)](https://cran.r-project.org/package=osmapiR)
[![](https://badges.ropensci.org/633_status.svg)](https://github.com/ropensci/software-review/issues/633)
<!-- badges: end -->

Implements [OpenStreetMap API](https://wiki.openstreetmap.org/wiki/API_v0.6) for R.

You are responsible for following the [API Usage Policy](https://operations.osmfoundation.org/policies/api/).
You can modify the user agent of the requests by setting the option `osmapir.user_agent`:
```r
options(osmapir.user_agent = "my new user agent")
```

## Installation

You can install the development version of osmapiR from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("jmaspons/osmapiR") # Without vignettes

## With vignettes (also accessible at https://jmaspons.github.io/osmapiR/ > Articles)
# install.packages("rmarkdown") # Needed to build vignettes.
remotes::install_github("jmaspons/osmapiR", build_vignettes = TRUE)
```

## Examples

This is a basic example which shows how to get map data:

```{r osm objects}
library(osmapiR)

# For testing edition without breaking the OSM data,
# make calls to `https://master.apis.dev.openstreetmap.org`

# set_osmapi_connection(server = "testing") # lacks data

bbox <- c(2.4166059, 42.5945594, 2.4176574, 42.5962101)

## Download objects by bounding box
osm_objs <- osm_bbox_objects(bbox = bbox, tags_in_columns = TRUE)

## View history of an object
sel <- osm_objs$`name:ca` %in% "Abadia de Sant Miquel de Cuixà"
obj <- osm_objs[sel, ]

obj_history <- osm_history_object(osm_type = obj$osm_type, osm_id = obj$osm_id) # tags in a list column
obj_history

# obj_history$tags
```


Get notes:
```{r notes}
notes <- osm_read_bbox_notes(bbox = bbox, closed = -1)
notes

# notes$comments
```


Get GPX data:
``` r
## Requires authentication
usr_traces <-  osm_list_gpxs()
osm_get_gpx_metadata(gpx_id = 3790367)
osm_get_data_gpx(gpx_id = 3790367, format = "R")
```
```{r gpx}
gpx <- osm_get_points_gps(bbox = bbox)
gpx
```


## Related packages

* [osmdata](https://cran.r-project.org/package=osmdata) implements the Overpass API to query data from OSM.
* [osmextract](https://cran.r-project.org/package=osmextract) matches, downloads, converts and imports bulk OSM data
  (`.pbf` files)
* [OpenStreetMap](https://cran.r-project.org/package=OpenStreetMap) Accesses high resolution raster maps using the
  OpenStreetMap protocol.
  
`osmapiR` is the only package to access other OSM data than the maps data (map notes, GPS traces, changelogs and
users). It can be also useful to get the history of the OSM objects and is the only package that allows editing and
upload any kind of data.

To access the OSM map data for purposes other than editing or exploring the history of the objects, perhaps is better to
use the other packages that implements the Overpass API ([osmdata](https://cran.r-project.org/package=osmdata)) or
that works with `.pbf` files ([osmextract](https://cran.r-project.org/package=osmextract)).

## Code of Conduct

Please note that the osmapiR project is released with a
[Contributor Code of Conduct](https://jmaspons.github.io/osmapiR/CODE_OF_CONDUCT.html). By contributing to this project,
you agree to abide by its terms.
